### 2015-05-22 results.tex
ping bench as line plot

\section{Response time -- latency}

\begin{figure}[ht]
\input{graphs/ipsec-ping-benchmark}
\caption{Ping min/avg/max response time}{for different packet sizes using IPsec. For each packet size, 1000 requests were flooded to the board, that is \textit{"outputs packets as fast as they come back or one hundred times per second, whichever is more"}, according to the \texttt{ping} command manual.}
\label{fig:ping-benchmark-ipsec}
\end{figure}

@@

>>>>

@@

\section{Response time -- latency}
After the establishement of a connection.

\begin{figure}[ht]
\input{graphs/ipsec-ping-benchmark}
\caption{Ping min/avg/max response time}{for different packet sizes using IPsec. For each packet size, 1000 requests were flooded to the board, that is \textit{"outputs packets as fast as they come back or one hundred times per second, whichever is more"}, according to the \texttt{ping} command manual.} %TODO move the end of the caption to the "test protocol" chapter.
\label{fig:ping-benchmark-ipsec}
\end{figure}
